\rule{350pt}{5pt}\\ \textbf{An Extension of Optimal Teaching For Online Perceptrons} \\ \rule{350pt}{1pt}

### 2017-05-04 paper_final.tex

\section{Introduction}
In the real world, there are often scenarios where a teacher wishes to
embed a desired concept within a learner. Sometimes, the teacher can only
interact with the learner by providing the learner with a set of training examples.
The task of creating the smallest possible set of examples that
produces the desired concept in the learner is known as optimal teaching
\cite{machine_teaching} \cite{teaching_dimension}. \cite{perceptron} looked for
the first time at optimal teaching in an online environment by proving the
optimal teaching dimension in an online Perceptron. In this paper we look at the
optimal teaching of the same perceptron, but with a teacher that also possess
the ability to use unlabeled examples. An unlabeled example gives the teacher
knowledge of the learner's prediction about that example without altering the
learner's state. This is a reasonable power for any real-world teacher to
posses. We show that this added ability allows the teacher to teach an
online perceptron in a zero-knowledge scenario that otherwise would have been
difficult.

@@

>>>>

\section{Introduction}
====
Mine

In the real world, there are often scenarios where a teacher wishes to
embed a desired concept within a learner. Sometimes, the teacher can only
interact with the learner by providing the learner with a set of training examples.
The task of creating the smallest possible set of examples that
produces the desired concept in the learner is known as optimal teaching
\cite{machine_teaching} \cite{teaching_dimension}. \cite{perceptron} looked for
the first time at optimal teaching in an online environment by proving the
optimal teaching dimension in an online Perceptron. In this paper we look at the
optimal teaching of the same perceptron, but with a teacher that also possess
the ability to use unlabeled examples. An unlabeled example gives the teacher
knowledge of the learner's prediction about that example without altering the
learner's state. This is a reasonable power for any real-world teacher to
posses. We show that this added ability allows the teacher to teach an
online perceptron in a zero-knowledge scenario that otherwise would have been
difficult.

@@

====
Yours

There may be a scenario where one entity, or the \textit{teacher},  has a desired target concept and a learner in which the teacher wants to embed that concept. In this scenario the teacher can only interact with the learner by constructing and then giving the learner a set of training examples. This constructive task is known as optimal teaching \cite{machine_teaching} \cite{teaching_dimension}. It has applications in education and security \cite{security}\cite{education} \cite{poisoning}. \cite{perceptron}\cite{td_linear} looked for the first time at online teaching in an online environment, with an online perceptron. In this paper we look at optimal teaching of the same perceptron, but now we give the teacher the ability to use unlabeled examples. Unlabeled examples allow the teacher to probe to discover more about the learners current state while not changing the learner. We show that this new added ability allows the teacher to teach an online perceptron in a scenario, that before may have been difficult.

The specific perceptron we are teaching is the  online perceptron \cite{perceptron_algo}. The algorithm is designed for a binary classification. It can learn any linear decision boundary,
with mapping $x \to sign(\langle w, x \rangle)$ where $x \in \mathbb{R}^d$ comes from the input space and $w \in \mathbb{R}^d$ parameterizes the perceptron. Here , as in \cite{perceptron}, $sign(0) = -1$ for completeness. The learning algorithm for the online perceptron is seen below.

====
